An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/abs.tex
config: abs

\app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including ordering errors, fine-grained value correlation errors, 
entry missing errors, and environment-related errors. 
%Our tool, named \app, relies on an abstract representation of language 
%rules to allow for this modularity. 
\ennan{One or two sentences here describe the most important
experimental results. For example, we verify real-world misconfiguration 
files and find 95\% errors are detected.}

>>>>

\app is capable of detecting various tricky errors that cannot
be detected by previous efforts,
including ordering errors, fine-grained value correlation errors, 
entry missing errors, and environment-related errors. 
Our experiment shows \app is able to detect 83\% errors from
a real-world dataset with 261 incorrect MySQL configuration files.
